\bf\mftitle

### 2011-03-01 doc/jInfer/base/base.tex
fixed overfull hboxes by package names
3187368 - Review documentation: cleanup - base done

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer: & Matej Vitásek \\ \hline
Required tokens:       & none \\ \hline
Provided tokens:       & none \\ \hline
Module dependencies:   & none \\ \hline
Public packages:       & cz.cuni.mff.ksi.jinfer.base.automaton \\ 
& cz.cuni.mff.ksi.jinfer.base.interfaces \\ 
& cz.cuni.mff.ksi.jinfer.base.interfaces.inference \\ 
& cz.cuni.mff.ksi.jinfer.base.interfaces.nodes \\
& cz.cuni.mff.ksi.jinfer.base.objects \\ 
& cz.cuni.mff.ksi.jinfer.base.objects.nodes \\ 
& cz.cuni.mff.ksi.jinfer.base.regexp \\ 
& cz.cuni.mff.ksi.jinfer.base.utils \\
& org.apache.log4j.* \\ \hline
\end{tabular}

@@

Regular expression representation is contained in \code{cz.cuni.mff.ksi.jinfer.base.regexp} package. Most important class is of course \code{Regexp}, assisted by an enum of its type \code{RegexpType} and representation of its interval \code{RegexpInterval}.\\
XML node representation is described by interfaces in \code{cz.cuni.mff.ksi.jinfer.base.interfaces.nodes} package and more-less concrete implementations in \code{cz.cuni.mff.ksi.jinfer.base.objects.nodes} package.\\
Finite state automata representation is contained in the \code{cz.cuni.mff.ksi.jinfer.base.automaton} package.\\
Refer to \cite{archdoc} to get an accurate description of all these representations.\\

>>>>

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer & Matej Vitásek \\ \hline
Required tokens       & none \\ \hline
Provided tokens       & none \\ \hline
Module dependencies   & none \\ \hline
Public packages       & \code{cz.cuni.mff.ksi.jinfer.base.automaton} \\ 
& \code{cz.cuni.mff.ksi.jinfer.base.interfaces} \\ 
& \code{cz.cuni.mff.ksi.jinfer.base.interfaces.inference} \\ 
& \code{cz.cuni.mff.ksi.jinfer.base.interfaces.nodes} \\
& \code{cz.cuni.mff.ksi.jinfer.base.objects} \\ 
& \code{cz.cuni.mff.ksi.jinfer.base.objects.nodes} \\ 
& \code{cz.cuni.mff.ksi.jinfer.base.regexp} \\ 
& \code{cz.cuni.mff.ksi.jinfer.base.utils} \\
& \code{org.apache.log4j.*} \\ \hline
\end{tabular}

@@

Regular expression representation is contained in \code{cz.cuni.mff.ksi.jinfer.base.regexp} package. Most important class is of course \code{Regexp}, assisted by an enum of its type \code{RegexpType} and representation of its interval \code{RegexpInter\.val}.\\
XML node representation is described by interfaces in \code{cz.cuni.mff.ksi.jinfer.base.interfaces.nodes} package and more-less concrete implementations in \code{cz.cuni.mff.ksi.jinfer.base.objects.nodes} package.\\
Finite state automata representation is contained in the \code{cz.cuni.mff.ksi.jinfer.base.automaton} package.\\
Refer to \cite{archdoc} to get an accurate description of all these representations.\\
